Optimal Finite Element Integration

### 2015-07-30 TOMS_Paper/assembly.tex
Before refactoring to global reasoning

The intuition of the algorithm to synthesize an optimal loop nest is shown in Figure~\ref{code:intuition}.

@@

Before elaborating on how we determine the pre-evaluation gain (or loss), we demonstrate the optimality of the approach.
%We introduce the following notation ...

@@

B) This holds due to a simple observation. In the absence of sharing, the statement is trivially true since we would have $LN_{ops_2}' > LN_{ops_2}$ and we are assuming that pre-evaluation was optimal for the monomials at hand. In the worst case, instead, all non pre-evaluated monomials share terms with those in $Z$. Anyway, the best we can do

%: regardless of whether there is sharing between terms in $Z_P$ and $\overline{Z} = Z \setminus Z_P$, then the statement is trivially true, since we are assuming that $Z$ contains all monomials for which pre-evaluation is sub-optimal. If, on the other hand, $\delta \in Z_P \cap \overline{Z}$, one can reason as follows. We can first remove sharing; this makes  to reach local optimality and we compare the operation counts. the cost of the loop nest would be $Z_P^{pre} + P + \sharp L_i \cdot Z \setminus Z_P$, which is greater than $...$, since $Z_P^{pre} > \sharp L_i \cdot Z_P$.

\end{proof}

>>>>

The intuition of the main algorithm for optimal loop nest synthesis is shown in Figure~\ref{code:intuition}.

@@

Before elaborating on how we determine the pre-evaluation gain (or loss), we demonstrate the optimality of the approach.

@@

B) In the absence of sharing, the statement is trivially true since we would have $LN_{ops_2}' > LN_{ops_2}$ and we are starting from the assumption that pre-evaluation is optimal for the monomials considered. As opposed to this extreme case, there could be some degree of sharing between monomials in $P_Z$ an $\overline{P}$. However, as clarified in the next section, this situation is not possible: the cost function "sees sharing" and it would prevent pre-evaluation by counting on sharing-removal for optimality. Finally, partial sharing. Note that by not pre-evaluating $P_Z$, the following: $LN_{ops_1} - LN_{ops_1}' < LN_{ops_2}' - LN_{ops_2}$ trivially holds (i.e., the loss in operation count is larger than the gain). At best, once sharing is remove, 
\end{proof}

\subsection{Operation Counting}
